18.821 Project 2

### 2014-10-25 paper/paper.tex
Paper additions

>>>>

\section{Avoidance of permutations of $T_n$}
We now impose further restrictions on the set of permutations $S_n$. This new set of permutations, $T_n$ is defined follows.

\begin{definition}
For even $n$, $T_n$ is defined as the set of all permutations $\sigma \in S_n$ for which $1,3,5,\ldots,2n-1$ appear in increasing order, and $2i$ always appears to the right of $2i-1$.
\end{definition}

Since $T_n$ is only defined for even $n$, henceforth we shall refer to $T_n$ as $T_{2m}$ where $m$ is any integer greater than or equal to $0$.

Given the above definition of $T_{2m}$, we prove the following result about the cardinality of $T_{2m}$.

\begin{theorem}
$|T_{2m}| = 1 \cdot 3 \cdot 5 \cdot \ldots \cdot (2m-1)$
\end{theorem}

\begin{proof}
Observe that since $1,3,5,\ldots,2m-1$ must appear in increasing order in $T_{2m}$, our problem is now reduced to determining the relative order of $2,4,6,\ldots,2m$ with respect to each other, as well as with respect to $1,3,5,\ldots,2m-1$.

Let us first try to insert $2m$ into the sequence $1,3,5,\ldots,2m-1$. Clearly, the way $T_{2m}$ is defined, $2m$ can be inserted into only $1$ slot, the one following $2m-1$. (Here we define a slot as a gap between two existing elements of the sequence, or the gap that follows the last element of the sequence or the gap that precedes the first element of the sequence)

Now, let us try to insert $(2m-2)$ into the sequence. $(2m-2)$ can be inserted into $3$ slots in the sequence -- the one between $2m-3$ and $2m-1$, the one between $2m-1$ and $2m$ or the one following $2m$.

Now, if we try to insert $(2m-4)$ into this incompletely formed sequence, we will see that there are $5$ possible locations into which this number can be inserted. Continuing this for all even numbers upto $2$, we observe that the total number of ways such a sequence can  be created is equal to $1 \cdot 3 \cdot 5 \cdot \ldots \cdot (2m-1)$, as desired.
\end{proof}
